---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ggsimplestats

<!-- badges: start -->
[![R-CMD-check](https://github.com/maximilian-heeg/ggsimplestats/workflows/R-CMD-check/badge.svg)](https://github.com/maximilian-heeg/ggsimplestats/actions)
<!-- badges: end -->

The goal of ggsimplestats is to provide an easy interface to add statistics to boxplot 
created with ggplot2

## Installation

You can install the development version of ggsimplestats like so:

``` r
# install.packages("devtools")
devtools::install_github("maximilian-heeg/ggsimplestats")
```

## Minimal Example

This is a minimal example of how to add the statistics to a plot. In this example we use the `PlantGrowth` dataset.

```{r example, warning=FALSE}
library(ggplot2)
library(ggsimplestats)

theme_set(ggthemes::theme_few())

ggplot(PlantGrowth, aes(group, weight, fill=group)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest()
```


## Test types

Currently, four different tests are supported. 

- Two parametric tests
  - `stat_tukeyHSD` performes a TukeyHSD posthoc test on a anova.
  - `stat_mixedModel` creates a mixed model with  `lmer` using `y ~ x + (1|group)`.  
     In a second step, significanes are calcuated using `pairs(emmeans(model ~ x))`.
- Two non-parametric tests
  - `stat_kwAllPairsDunnTest` uses `PMCMRplus::kwAllPairsDunnTest()` to perform Dunn's non-parametric all-pairs comparison test for Kruskal-type ranked data
  - `stat_frdAllPairsNemenyiTest` uses `PMCMRplus::frdAllPairsNemenyiTest()` to perform Nemenyi's all-pairs comparisons tests of Friedman-type ranked data


## Further reading

For further information please see the `vignette("ggsimplestats")`.
