---
title: "Basic usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```



```{r setup}
library(ggplot2)
library(ggsimplestats)

theme_set(ggthemes::theme_few())
```


## Minimal Example

This is a minimal example of how to add the statistics to a plot. In this example we use the `PlantGrowth` dataset.

```{r example, warning=FALSE}
ggplot(PlantGrowth, aes(group, weight, fill=group)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest(vjust = -0.2)
```


## Test types

Currently, four different tests are supported. 

- Two parametric tests
  - `stat_tukeyHSD()` performes a TukeyHSD posthoc test on a anova.
  - `stat_mixedModel()` creates a mixed model with  `lme4::lmer()` using `y ~ x + (1|group)`.  
     In a second step, significanes are calcuated using `graphics::pairs(emmeans::emmeans(model ~ x))`.
- Two non-parametric tests
  - `stat_kwAllPairsDunnTest()` uses `PMCMRplus::kwAllPairsDunnTest()` to perform Dunn's non-parametric all-pairs comparison test for Kruskal-type ranked data
  - `stat_frdAllPairsNemenyiTest()` uses `PMCMRplus::frdAllPairsNemenyiTest()` to perform Nemenyi's all-pairs comparisons tests of Friedman-type ranked data


### TukeyHSD

Uses an Anova with TukeyHSD as a parametric test

```{r TukeyHSD}
ggplot(PlantGrowth, aes(group, weight, fill=group)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -0.2)
```



### Mixed model

```{r MixedModel}
df <- data.frame(patient=as.factor(rep(1:5, each=4)),
                 drug=as.factor(rep(1:4, times=5)),
                 response=c(30, 28, 16, 34,
                            14, 18, 10, 22,
                            24, 20, 18, 30,
                            38, 34, 20, 44,
                            26, 28, 14, 30))
ggplot(df, aes(x=drug, y=response, color=patient)) +
  geom_line(aes(group = patient)) +
  geom_point() +
  stat_mixedModel(aes(group = patient),
                  vjust = -0.2,
                  step.increase = 0.06)
```



### Dunn's non-parametric all-pairs

```{r Dunn, warning=FALSE}

ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest(vjust = -.2)

```

### Nemenyi's all-pairs comparisons tests

```{r Nemenyi}
df <- data.frame(patient=as.factor(rep(1:5, each=4)),
                 drug=as.factor(rep(1:4, times=5)),
                 response=c(30, 28, 16, 34,
                            14, 18, 10, 22,
                            24, 20, 18, 30,
                            38, 34, 20, 44,
                            26, 28, 14, 30))
ggplot(df, aes(x=drug, y=response, color=patient)) +
  geom_point(position = position_dodge(width = .2)) +
  stat_frdAllPairsNemenyiTest(aes(group = patient),
                              vjust = -0.2)
```


## Change format of p-value

If wanted, the format of the p value / label can be changed. The default uses `scales::pvalue`. To format the p values as 'stars' we can. e.g. use the `stars.pval` function from `gtools`

```{r change-p-value-format, warning=FALSE}
ggplot(PlantGrowth, aes(group, weight, fill=group)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest(format.fun = gtools::stars.pval, 
                          size = 15,
                          vjust = .3)
```

Or you can pass a lambda function to create a custom label.

```{r p-value-lambda-function, warning=FALSE}
ggplot(PlantGrowth, aes(group, weight, fill=group)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest(format.fun = \(x) {glue::glue('my p-value {scales::pvalue(x)}')},
                          vjust = -.2)
```


## Facets

All functions calculate the statistics for each panel of the plot individually and
can easily be used with facets.

```{r kw-facet, warning=FALSE}

ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_kwAllPairsDunnTest(vjust = -.2,
                          step.increase = 0.06) +
  facet_grid(~sex)

```


`stat_tukeyHSD` works with facets too.

```{r tukey-facet}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.06) +
  facet_grid(~sex)
```

## Further options


For further customization options please see `vignette("options")`
