---
title: "Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

```{r setup}
library(ggplot2)
library(ggsimplestats)

theme_set(ggthemes::theme_few())
```


This vignette shows the options that are available for all functions to customize the results.



## Step.increase


`step.increase` changes the space between two brackets. Sometimes it is then necessary to expand the scales. This can e.g. be done with `scale_y_continuous(expand = expansion(mult = c(0.05,0.15)))`

```{r step.increase}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.2,
                format.fun = \(x) {glue::glue('parametric p-value\n{scales::pvalue(x)}')}) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0.05,0.15)))
```


## Colour


`colour` changes the colour of the bracket and the label.

```{r change-colour}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.08,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')},
                colour = 'darkred') +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0.05,0.15)))
```


## Tick length

Use `tick.length` to control the length of the ticks of the brackets. 


```{r tick-length-1}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.12,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')},
                tick.length = 0.05) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15)))
```

Use `0` to remove them.

```{r tick-length-0}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.05,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')},
                tick.length = 0) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15)))
```

## Text adjustment

Use `vjust` to control the the vertical adjustment of the text. 


```{r vjust}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -1,
                step.increase = 0.12,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')}) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15))) +
  ggtitle('Big gap')

ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = 1.2,
                step.increase = 0.12,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')}) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15))) +
  ggtitle('Text below')
```

## Text size

Use `size` to control the the text size 


```{r size}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(size = 5,
                step.increase = 0.12,
                vjust = -.2,
                format.fun = \(x) {glue::glue('p: {scales::pvalue(x)}')}) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15))) +
  ggtitle('Tiny text')

ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(size = 20,
                step.increase = 0.12,
                vjust = -.2,
                format.fun = \(x) {glue::glue('{scales::pvalue(x)}')}) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15))) +
  ggtitle('Giant text')
```

## Show all p-values

Use `hide.ns` to to remove non-significant p values (cutoff `0.05`). Default is `TRUE`. Set `hide.ns=FALSE` to show all p-values.


```{r hide-ns}
ggplot(na.omit(palmerpenguins::penguins), aes(species, bill_length_mm, fill=species)) +
  geom_boxplot()  +
  stat_tukeyHSD(vjust = -.2,
                step.increase = 0.08,
                hide.ns = FALSE) +
  facet_grid(~sex) +
  scale_y_continuous(expand = expansion(mult = c(0,0.15))) +
  ggtitle('All p-values')

```

